---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
    ```
    if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
    ```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 

## Package installation
```{r, message=FALSE, warning=FALSE, eval=FALSE}
#install.packages("janeaustenr")  # for book by janeaustenr
#install.packages("gutenbergr")  # for free ebooks
#install.packages("dplyr")  # for data manipulation
#install.packages("stringr")  # for string manupulation
#install.packages("tidytext")  # for text mining
#install.packages("SnowballC") # for text stemming
#install.packages("ggplot2")  # for text stemming
#install.packages("wordcloud") # word-cloud generator 
#install.packages("RColorBrewer") # color palettes

if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("bradleyboehmke/harrypotter")
```

## Loading required packages
```{r message=FALSE, warning=FALSE}
library(janeaustenr)
library(gutenbergr)
library(dplyr)
library(stringr)
library(tidytext)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)
library(harrypotter)

```

## Merging data from different sources
Let’s start with that, and also use mutate() to annotate a linenumber quantity to keep track of lines in the original format and a chapter (using a regex) to find where all the chapters are.
```{r}

# Fetch Book metadata from theGuardian.com e.g publisher, ranking, sales, author e.t.c 
bookMetadata <- read.csv("https://docs.google.com/spreadsheets/d/1dhxblR1Vl7PbVP_mNhwEa3_lfUWiF__xSODLq1W83CA/export?format=csv&id=1dhxblR1Vl7PbVP_mNhwEa3_lfUWiF__xSODLq1W83CA&gid=0")

# Combine all The Harry Potter books into 1 dataframe and add column which will be used a reference "Title"

book1 <- data_frame(Title="Harry Potter and the Philosopher's Stone", text=philosophers_stone)
book2 <- data_frame(Title="Harry Potter and the Chamber of Secrets", text=chamber_of_secrets)
book3 <- data_frame(Title="Harry Potter and the Prisoner of Azkaban", text=prisoner_of_azkaban)
book4 <- data_frame(Title="Harry Potter and the Goblet of Fire", text=goblet_of_fire)
book5 <- data_frame(Title="Harry Potter and the Order of the Phoenix", text=order_of_the_phoenix)
book6 <- data_frame(Title="Harry Potter and the Half-blood Prince", text=half_blood_prince)
book7 <- data_frame(Title="Harry Potter and the Deathly Hallows", text=deathly_hallows)

# Join BookMetadata and HarryPotter dfs by "Title"
harrypotterSeries <- rbind(book1,book2, book3, book4, book5, book6, book7) %>% inner_join(bookMetadata, by = "Title")%>%
  group_by(Title) %>%
  mutate(Chapter = row_number())%>% # add chapter
  ungroup()

head(harrypotterSeries)
```

## Cleaning Data
1. Restructure it in the one-token-per-row format, 

```{r}
harrypotter_tokenized <- harrypotterSeries %>%
  unnest_tokens(word, text)

harrypotter_tokenized %>%
  select(Title, Chapter, word) %>%
  head()

```

2. Remove stop words; stop words are words that are not useful for an analysis, typically extremely common words such as "the", "of", "to",

```{r}
harrypotter_clean_tokens <- harrypotter_tokenized %>% 
   anti_join(stop_words)  #remove stop words like "the"
```

## Perfrom Analysis by answereing the following questions
1. what is the most important charecter based on how much is whas mentioned 
2. what is the most scariest book based on sentiment analysis ?

```{r}
harrypotter_clean_tokens%>%
  inner_join(get_sentiments("bing"), by = "word") %>% # join sentiment
  group_by(Title)%>% # make each row  abook
  count(sentiment, sort = TRUE)%>% # count sentiment
  filter(sentiment=="negative")  #filter by negative sentiment

# Using bing lexicon, Harry Potter and the Order of the Phoenix is the scariest with about 8k negative sentiments

```




3. What the top ten used words in exception to stop words ?
```{r}
word_count <- harrypotter_clean_tokens %>% 
  count(word, sort = TRUE) %>% 
   mutate(word = reorder(word, n))
head(word_count)
```

 
```{r}
# Visualization of the most common words
word_count_gt_600 <- word_count %>%
  filter(n > 600)



# plot using word cloud
 
  wordcloud(words = word_count_gt_600$word, freq = word_count_gt_600$n, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

***Sentimental Analysis
```{r}

```

