---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
    ```
    if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")
    ```
- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 
```{r, message=FALSE, warning=FALSE, eval=FALSE}
#install.packages("janeaustenr")  # for book by janeaustenr
#install.packages("gutenbergr")  # for free ebooks
#install.packages("dplyr")  # for data manipulation
#install.packages("stringr")  # for string manupulation
#install.packages("tidytext")  # for text mining
#install.packages("SnowballC") # for text stemming
#install.packages("ggplot2")  # for text stemming
#install.packages("wordcloud") # word-cloud generator 
#install.packages("RColorBrewer") # color palettes

```


```{r message=FALSE, warning=FALSE}
library(janeaustenr)
library(gutenbergr)
library(dplyr)
library(stringr)
library(tidytext)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)


```
Let’s start with that, and also use mutate() to annotate a linenumber quantity to keep track of lines in the original format and a chapter (using a regex) to find where all the chapters are.
```{r}
#cleaning data
# Convert the text to lower case
# Remove english common stopwords eg the, for, e.t.c
original_books <- austen_books() %>%
  group_by(book) %>%
  mutate(linenumber = row_number(),
         chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]",
                                                 ignore_case = TRUE)))) %>%
  ungroup()

original_books
```
restructure it in the one-token-per-row format, 

```{r}
tidy_books <- original_books %>%
  unnest_tokens(word, text)

tidy_books
```

remove stop words; stop words are words that are not useful for an analysis, typically extremely common words such as "the", "of", "to",

```{r}
data(stop_words)

tidy_books <- tidy_books %>%
  anti_join(stop_words)
```

find the most common words in all the books as a whole.
```{r}
tidy_books %>%
  count(word, sort = TRUE) 
```

create a visualization of the most common words 
```{r}
# plot using ggplot
word_count <- tidy_books %>%
  count(word, sort = TRUE) %>%
  filter(n > 600) %>%
  mutate(word = reorder(word, n))



# plot using word cloud
 
  wordcloud(words = word_count$word, freq = word_count$n, min.freq = 1,
          random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2"))

```

***Sentimental Analysis
```{r}

```

